---
title: "Lab 01 - Hello R"
author: "Heather Hawkins"
date: "01/12/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1
##### Datasaurus Dozen

1846 rows and 3 columns 

3 variables: 

dataset: indicates which dataset the data are from

x: x-values

y: y-value

### Exercise 2

Plotted data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotted data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset=="star")
ggplot(data=star_data, mapping=aes(x=x,y=y))+
  geom_point()
```

Correlation of 'x' and 'y' for star_data

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

R seems to be less than the dino_dataset. -0.0015

### Exercise 4

Plotted data for circle_data

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset=="circle")
ggplot(data=circle_data, mapping=aes(x=x,y=y))+
  geom_point()
```

Correlation for 'x' and 'y' for circle_dataset 
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

Compared to dino_data, circle data's r value is 0.038 more 

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.



## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
