---
title: "Lab 01 - Hello R"
author: "Heather Hawkins"
date: "01/12/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

---
---
---

### Exercise 1

##### Datasaurus Dozen

1846 rows and 3 columns

3 variables:

dataset: indicates which dataset the data are from

x: x-values

y: y-value

### Exercise 2

Plotted data in the dino dataset:

```{r plot-dino, fig.height=5, fig.width=7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset:

```{r cor-dino, fig.height=5, fig.width=7}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotted data in the star dataset:

```{r plot-star, fig.height=5, fig.width=7}
star_data <- datasaurus_dozen %>%
  filter(dataset=="star")

ggplot(data=star_data, mapping=aes(x=x,y=y))+
  geom_point()
```

Correlation of 'x' and 'y' for star_data

```{r cor-star, fig.height=5, fig.width=7}
star_data %>%
  summarize(r = cor(x, y))
```

R seems to be less than the dino_dataset. (0.0015 less)

### Exercise 4

Plotted data for circle_data

```{r plot-circle, fig.height=5, fig.width=7}
circle_data <- datasaurus_dozen %>%
  filter(dataset=="circle")

ggplot(data=circle_data, mapping=aes(x=x,y=y))+
  geom_point()
```

Correlation for 'x' and 'y' for circle_dataset

```{r cor-circle, fig.height=5, fig.width=7}
circle_data %>%
  summarize(r = cor(x, y))
```

Compared to dino_data, circle data's r value is slightly bigger (0.0038 more)

### Exercise 5

Plot of all datasets

```{r all plots, fig.height=10, fig.width=7}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Every dataset's correlation coefficients

```{r All correlations, echo=TRUE, fig.height=5, fig.width=7}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
